---
title: "US Capital Flows"
output: 
  html_document:
    css: www/company-styles.css
    toc: true
editor_options: 
  chunk_output_type: console
---

<style type="text/css">

div.main-container {
  max-width: 1400px;
  margin-left: auto;
  margin-right: auto;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```



```{r load packages, include=FALSE}

library(vctrs)
library(tidyverse)
library(lubridate)
library(dplyr)
library(ggplot2)
library(scales)
library(tidyr)
library(kableExtra)
library(DBI)
library(odbc)
library(plotly)
library(here)
library(zoo)

# source("00 Data Import.R")
# source("01 US Econ Data.R")
# source("02 AU Econ Data.R")
# source("10 US Summary.R")
# source("20 AU Summary.R")


load(here("data-edited","Foreign securities held by U.S. residents - outflows.Rda"))
load(here("data-edited","Foreign securities held by U.S. residents - outflows (SUMMARY).Rda"))
load(here("data-edited","U.S. securities held by foreign residents.Rda"))
load(here("data-edited","U.S. securities held by foreign residents (SUMMARY).Rda"))


################# Sparkline functions:
round_0 <- function(x) round(x, digits = 0)
round_1 <- function(x) round(x, digits = 1)
last_round_1 <- function(x) dplyr::last(x) %>% round_1()
last_round_0 <- function(x) dplyr::last(x) %>% round_0()

```


# U.S. Aggregate Portfolio Holdings and Transactions											

Mar 2021 Data -- There is an issue with the months (I think)


## Foreign securities held by U.S. residents {.tabset .tabset-pills}

All amounts are stated in **USD $billions** unless other wise noted

### Portfolio value and Net Capital Flows
```{r US Foreign NET, echo=FALSE, warning=FALSE, message=FALSE}
#Sparklines Data
library(formattable)
library(sparkline)
library(DT)
library(reshape2)


date <- format(max(US_Res_Holding_of_FR_Sec$Month)
               , "%b %Y")


US_Res_Holding_of_FR_Sec_Summ$variable <- as.character(US_Res_Holding_of_FR_Sec_Summ$variable)
#US_Res_Holding_of_FR_Sec_Summ <- separate(US_Res_Holding_of_FR_Sec_Summ, "variable", c("Instrument", "Transaction"), "_")

temp <- t(US_Res_Holding_of_FR_Sec[1,c(12,14,16)]) # Pull data for Total,Bond,Stocks (12m rolling average, most recent month) and transpose
temp <- temp[ order(row.names(temp)), ] # reorder alphabetically
temp <- as.data.frame(temp) # convert tot a dataframe
colnames(temp) <- c("12m_cum") #rename column
rownames(temp) <- NULL # remove row names

temp5 <- t(US_Res_Holding_of_FR_Sec[1,c(4:6)])
temp5 <- temp5[ order(row.names(temp5)), ] # reorder alphabetically
temp5 <- as.data.frame(temp5) # convert tot a dataframe
colnames(temp5) <- c("Mkt Value (This Month)") #rename column
rownames(temp5) <- NULL # remove row names

temp1 <- cbind(
  US_Res_Holding_of_FR_Sec_Summ %>% #[c(1,6,7)] # Pull Summary data
  separate("variable", c("Instrument", "Transaction"), "_") %>% #split desriptive column into two for categorisation
  filter(Transaction == "Flows") # Filter to only give data on net flows (not gross buy/sell)
  , temp) %>% # use cbind to combine dat from Summ table and 12m rolling average data from `temp`
  select(Instrument, value, zscore, `12m_cum`) %>% #restrict to wanted columns
  mutate(value = format(round(value), big.mark=",") ## format output (number of d.p.)
         , zscore = format(round(zscore, 2L), nsmall = 2L)
         , `12m_cum` = format(round(`12m_cum`), big.mark=",")
          ) %>%
  rename( "Net Capital Flows (This Month)" = "value" #rename columns for output
         , "Current Month Z-Score" = "zscore"
         , "Net Capital Flows (12 months)" = "12m_cum")



temp <- US_Res_Holding_of_FR_Sec[c(1:12),c(3,4:9,12,14,16)] %>% #Pull first 12 row (most recent year of data), and specific columns (Total mkt value, Total flows, 12m rolling avg of flows)
  `colnames<-`(c("Month", "Total_Mkt", "Bonds_Mkt", "Stocks_Mkt", "Total_Flow", "Bonds_Flow", "Stocks_Flow", "Total_12mR", "Bonds_12mR", "Stocks_12mR")) %>% # rename columns for data 
  melt(id.vars = "Month") %>% #reshape data into 3cols
  separate("variable", c("Instrument", "Transaction"), "_") %>% #split variable col into 2 with new names
  pivot_wider(names_from = Transaction, values_from = value) %>%# spread data into more cols for presentataion purposes
  group_by(Instrument) %>% #group by instrument 
  summarise(`Market Value (12 Months)` = spk_chr(round_1(Mkt), type = "line") # Sparkline shit
            , `Net Capital Flows (12 Months)` = spk_chr(round_1(Flow), type = "bar")
            , `12 Month Rolling Flows` = spk_chr(round_1(`12mR`), type = "line")
  ) 
temp[temp == "Stocks"] <- "Equity" #rename data for merging
temp1[temp1 == "Bond"] <- "Bonds" #rename data for merging


#Sparkline data ma since 2010
temp2 <- US_Res_Holding_of_FR_Sec[,c(1,13,15,17)] %>% 
  na.omit() %>%
  `colnames<-`(c("Month", "Total", "Bonds", "Equity")) %>%
  melt(id.vars = "Month") %>%
  `colnames<-`(c("Month", "Instrument", "value")) %>%
  group_by(Instrument) %>%
  summarise(`Net Flow 3m m.a.` = spk_chr(round_1(value), type = "line"))

#merge data and output table
temp <- cbind(
  merge(
    merge(temp1, temp)
    , temp2)
  , temp5)

temp[c(1,9,5,2,3,6,4,7,8)] %>%
  formattable() %>% 
  as.datatable() %>%
  spk_add_deps() 






################################################################################################ Example
# library(gapminder)
# 
# gapminder <- gapminder
# gapminder %>%
#   filter(continent == "Africa") %>% 
#   group_by(country) %>%
#   summarise(
#     `life expectancy` = spk_chr(round_1(lifeExp)),
#     `life expectancy (years)` = last_round_1(lifeExp),
#     `gdp per capita` = spk_chr(gdpPercap %>% round_0()),
#     `gdp per capita (USD)` = last_round_0(gdpPercap),
#     `population (M)` = last_round_1(pop / 1e6)
#   ) %>% 
#   formattable() %>% 
#   as.datatable() %>%
#   spk_add_deps() 
################################################################################################ 

```

### Gross Monthly Transactions 
```{r US Foreign GROSS, echo=FALSE, warning=FALSE, message=FALSE}


US_Res_Holding_of_FR_Sec_Summ$variable <- as.character(US_Res_Holding_of_FR_Sec_Summ$variable)
#US_Res_Holding_of_FR_Sec_Summ <- separate(US_Res_Holding_of_FR_Sec_Summ, "variable", c("Instrument", "Transaction"), "_")

US_Res_Holding_of_FR_Sec_Summ[c(1,6,2,7)] %>%
  separate("variable", c("Instrument", "Transaction"), "_") %>%
  filter(Transaction != "Flows") %>%
  mutate(value = format(round(value), big.mark=",")
         , mean = format(round(mean), big.mark=",")
         , zscore = format(round(zscore, 2L), nsmall = 2L)
          ) %>%
  rename(date = "value"
         , "24-Month Mean"  = "mean"
         , "Current Month Z-Score" = "zscore") %>%
  kable() %>%
  kable_styling(c("striped"))

# %>%
#   pivot_wider(names_from = Transaction, values_from = c("mean", "value", "zscore")) %>%
#   rename("This month (BUY)" = "value_Buy"
#          , "24-Month Mean (BUY)"  = "mean_Buy"
#          , "Current Month Z-Score (BUY)" = "zscore_Buy"
#          , "This month (SELL)" = "value_Sell"
#          , "24-Month Mean (SELL)"  = "mean_Sell"
#          , "Current Month Z-Score (SELL)" = "zscore_Sell") #%>%
#   kbl() %>%
#   kable_styling(c("striped"))

```










## U.S. securities held by foreign residents {.tabset .tabset-pills}

### Portfolio value and Net Capital Flows

```{r FR US NET, echo=FALSE, warning=FALSE, message=FALSE}

US_Sec_Held_by_FR_Summ$variable <- as.character(US_Sec_Held_by_FR_Summ$variable)
#US_Sec_Held_by_FR_Summ <- separate(US_Sec_Held_by_FR_Summ, "variable", c("Instrument", "Transaction"), "_")

temp <- t(US_Sec_Held_by_FR[1,c(12,14,16)]) # Pull data for Total,Bond,Stocks (12m rolling average, most recent month) and transpose
temp <- temp[ order(row.names(temp)), ] # reorder alphabetically
temp <- as.data.frame(temp) # convert tot a dataframe
colnames(temp) <- c("12m_cum") #rename column
rownames(temp) <- NULL # remove row names

temp5 <- t(US_Sec_Held_by_FR[1,c(4:6)])
temp5 <- temp5[ order(row.names(temp5)), ] # reorder alphabetically
temp5 <- as.data.frame(temp5) # convert tot a dataframe
colnames(temp5) <- c("Mkt Value (This Month)") #rename column
rownames(temp5) <- NULL # remove row names

temp1 <- cbind(
  US_Sec_Held_by_FR_Summ %>% #[c(1,6,7)] # Pull Summary data
  separate("variable", c("Instrument", "Transaction"), "_") %>% #split desriptive column into two for categorisation
  filter(Transaction == "Flows") # Filter to only give data on net flows (not gross buy/sell)
  , temp) %>% # use cbind to combine dat from Summ table and 12m rolling average data from `temp`
  select(Instrument, value, zscore, `12m_cum`) %>% #restrict to wanted columns
  mutate(value = format(round(value), big.mark=",") ## format output (number of d.p.)
         , zscore = format(round(zscore, 2L), nsmall = 2L)
         , `12m_cum` = format(round(`12m_cum`), big.mark=",")
          ) %>%
  rename( "Net Capital Flows (This Month)" = "value" #rename columns for output
         , "Current Month Z-Score" = "zscore"
         , "Net Capital Flows (12 months)" = "12m_cum")



temp <- US_Sec_Held_by_FR[c(1:12),c(1,4:9,12,14,16)] %>% #Pull first 12 row (most recent year of data), and specific columns (Total mkt value, Total flows, 12m rolling avg of flows)
  `colnames<-`(c("Month", "Total_Mkt", "Bonds_Mkt", "Stocks_Mkt", "Total_Flow", "Bonds_Flow", "Stocks_Flow", "Total_12mR", "Bonds_12mR", "Stocks_12mR")) %>% # rename columns for data 
  melt(id.vars = "Month") %>% #reshape data into 3cols
  separate("variable", c("Instrument", "Transaction"), "_") %>% #split variable col into 2 with new names
  pivot_wider(names_from = Transaction, values_from = value) %>%# spread data into more cols for presentataion purposes
  group_by(Instrument) %>% #group by instrument 
  summarise(`Market Value (12 Months)` = spk_chr(round_1(Mkt), type = "line") # Sparkline shit
            , `Net Capital Flows (12 Months)` = spk_chr(round_1(Flow), type = "bar")
            , `12 Month Rolling Flows` = spk_chr(round_1(`12mR`), type = "line")
  ) 
temp[temp == "Stocks"] <- "Equity" #rename data for merging
temp1[temp1 == "Bond"] <- "Bonds" #rename data for merging


#Sparkline data ma since 2010
temp2 <- US_Sec_Held_by_FR[,c(1,13,15,17)] %>% 
  na.omit() %>%
  `colnames<-`(c("Month", "Total", "Bonds", "Equity")) %>%
  melt(id.vars = "Month") %>%
  `colnames<-`(c("Month", "Instrument", "value")) %>%
  group_by(Instrument) %>%
  summarise(`Net Flow 3m m.a.` = spk_chr(round_1(value), type = "line"))

#merge data and output table
temp <- cbind(
  merge(
    merge(temp1, temp)
    , temp2)
  , temp5)

temp[c(1,9,5,2,3,6,4,7,8)] %>%
  formattable() %>% 
  as.datatable() %>%
  spk_add_deps() 


											
```


### Gross Monthly Transactions 

```{r FR US GROSS, echo=FALSE, warning=FALSE, message=FALSE}

US_Sec_Held_by_FR_Summ$variable <- as.character(US_Sec_Held_by_FR_Summ$variable)
#US_Sec_Held_by_FR_Summ <- separate(US_Sec_Held_by_FR_Summ, "variable", c("Instrument", "Transaction"), "_")

US_Sec_Held_by_FR_Summ[c(1,6,2,7)] %>%
  separate("variable", c("Instrument", "Transaction"), "_") %>%
  filter(Transaction != "Flows") %>%
  mutate(value = format(round(value), big.mark=",")
         , mean = format(round(mean), big.mark=",")
         , zscore = format(round(zscore, 2L), nsmall = 2L)
          ) %>%
  rename(date = "value"
         , "24-Month Mean"  = "mean"
         , "Current Month Z-Score" = "zscore") %>%
  kable() %>%
  kable_styling(c("striped"))

											
```

## U.S. Financial Market Indicators


<div class = "row">
<div class = "col-md-6">
```{r US Econ 1,  warning = FALSE, echo = FALSE, dev=c('svg')}


################ Load "01 US Econ Data.R"
load(here("data-edited","Trade Weighted U.S. Dollar Index.Rda"))
load(here("data-edited","Effective Federal Funds Rate.Rda"))
load(here("data-edited","Daily Treasury Yield Curve Rates.Rda"))
load(here("data-edited","SPX.Rda"))
load(here("data-edited","DJI.Rda"))
load(here("data-edited","NDX.Rda"))
load(here("data-edited","VIX.Rda"))
load(here("data-edited","U.S. 5-Year, 5-Year Forward Inflation Expectation Rate.Rda"))
load(here("data-edited","U.S. Bureau of Labor Statistics, Historical CPI-U.Rda"))


##################################### remove "( ... , 1) from the legend
clean_plotly_leg <- function(.plotly_x, .extract_str) {
  # Inpects an x$data list in a plotly object, cleans up legend values where appropriate
  if ("legendgroup" %in% names(.plotly_x)) {
    # The list includes a legend group
    .plotly_x$legendgroup <- stringr::str_extract(.plotly_x$legendgroup, .extract_str)
    .plotly_x$name <- stringr::str_extract(.plotly_x$name, .extract_str)
  }
  .plotly_x
}



ggplotly(
TW_USD %>%
  ggplot(aes(x = Date, y = Index)) +
  geom_line() +
  scale_fill_brewer(palette = "PuBu") +
  ggtitle("Trade-weighted USD Index") +
  theme_minimal() +
  theme(axis.title.x=element_blank()
        , axis.title.y=element_blank()
        , legend.title = element_blank()
        , legend.position = "bottom")
)



```
</div>
<div class = "col-md-6">
```{r US Econ 2, warning = FALSE, echo=FALSE, dev=c('svg')}


## Plot and remove shit from legend
temp <- ggplotly(
FedFundsRate %>%
  #melt(id.vars = "Date") %>%
  ggplot() +
  geom_ribbon(aes(x = date, ymin= Target_Min, ymax = Target_Max), fill= "blue", alpha = 0.3) +
  geom_line(aes(x = date, y = Eff_Rate)) +
  geom_line(aes(x = date, y = Eff_Rate
                , text = paste('Date: ', date,
                               '<br>Effective Rate: ', Eff_Rate,
                               '<br>Target (Min): ', Target_Min,
                               '<br>Target (Max): ', Target_Max
                               ))) +
  scale_fill_brewer(palette = "PuBu") +
  ggtitle("U.S. Federal Funds Rate") +
  theme_minimal() +
  theme(axis.title.x=element_blank()
        , axis.title.y=element_blank()
        , legend.title = element_blank()
        , legend.position = "bottom")
, tooltip = c("text"))

temp$x$data <-
  temp$x$data %>% 
  map(clean_plotly_leg, "[^\\(][^,]*") # ie remove the opening bracket, if one exists, and extract each character up to the first comma
temp
```
</div>
</div>







<div class = "row">
<div class = "col-md-6">
```{r US Econ 3,  warning = FALSE, echo = FALSE, dev=c('svg')}

temp <- ggplotly(
Yield_Curve_US %>%
  select("Date", "6m", "3y", "5y", "10y", "30y") %>%
  melt(id.vars = "Date") %>%
  ggplot() +
  geom_line(aes(x = Date, y = value
                , color = variable)) +
  geom_line(aes(x = Date, y = value
                , color = variable
                , text = paste('Date: ', Date,
                               '<br>Yield: ', value,
                               '<br>Instrument: ', variable
                               ))) +
  scale_fill_brewer(palette = "PuBu") +
  ggtitle("U.S. Treasury Benchmark Yields") +
  theme_minimal() +
  theme(axis.title.x=element_blank()
        , axis.title.y=element_blank()
        , legend.title = element_blank()
        , legend.position = "bottom")
, tooltip = c("text")) %>%
  layout(legend = 
           list(orientation = "h"
                , y=-0.1))

temp$x$data <-
  temp$x$data %>% 
  map(clean_plotly_leg, "[^\\(][^,]*") # ie remove the opening bracket, if one exists, and extract each character up to the first comma
temp

```
</div>
<div class = "col-md-6">
```{r US Econ 4, warning = FALSE, echo=FALSE, dev=c('svg')}


Hist_CPIU$`YoY % change` <- (Hist_CPIU$value/lag(Hist_CPIU$value, n= 12)-1)*100

ggplotly(
Hist_CPIU %>%
  ggplot(aes(x = date, y = `YoY % change`)) +
  geom_line() +
  scale_fill_brewer(palette = "PuBu") +
  ggtitle("U.S. CPI - YoY % change") +
  theme_minimal() +
  theme(axis.title.x=element_blank()
        , axis.title.y=element_blank()
        , legend.title = element_blank()
        , legend.position = "bottom")
)


```
</div>
</div>






<div class = "row">
<div class = "col-md-6">
```{r US Econ 5,  warning = FALSE, echo = FALSE, dev=c('svg')}

ggplotly(
FiveY_Fwd_Inflation_Exp %>%
  ggplot(aes(x = Date, y = Index)) +
  geom_line() +
  scale_fill_brewer(palette = "PuBu") +
  ggtitle("U.S. 5-years, 5-year Forward Inflation Expectations") +
  theme_minimal() +
  theme(axis.title.x=element_blank()
        , axis.title.y=element_blank()
        , legend.title = element_blank()
        , legend.position = "bottom")
)
```
</div>
<div class = "col-md-6">
```{r US Econ 6, warning = FALSE, echo=FALSE, dev=c('svg')}
temp <- ggplotly(
  DJI %>%
    merge(SPX, by = "date" , all = T) %>%
    merge(NDX, by = "date" , all = T) %>%
    na.omit() %>%
  `colnames<-`(c("Date","Dow Jones Industrial", "S&P500", "NASDAQ")) %>%
  melt(id.vars = "Date") %>%
  group_by(variable) %>%
   mutate(value = value/first(value))  %>%
  ggplot(aes(x = Date, y = value, color = variable)) +
  geom_line() +
  scale_fill_brewer(palette = "PuBu") +
  ggtitle("U.S. Stock Market Indices (rebased 100)") +
  theme_minimal() +
  theme(axis.title.x=element_blank()
        , axis.title.y=element_blank()
        , legend.title = element_blank()
        , legend.position = "bottom")
  ) %>%
  layout(legend = 
           list(orientation = "h"
                , y=-0.1))
temp$x$data <-
  temp$x$data %>% 
  map(clean_plotly_leg, "[^\\(][^,]*") # ie remove the opening bracket, if one exists, and extract each character up to the first comma
temp
```
</div>
</div>



\

Please contact [Joel Findlay](mailto:joel.findlay@gmail.com) if you have questions about the report.


